Behavior Driven Development in Haskell

### 2012-05-31 paper.tex
Motivate automatic spec discovery

\begin{quote}
    TBD:
\begin{itemize}
    \item \emph{optional:} Motivate why it's important to integrate
        Doctest with
        Cabal.

    \item \emph{optional:} Motivate \verb|hspec-discover|

        It is common to have several files that contain \emph{specs}.
        And we want to be able to run them all together.  Hspec allows
        us combine specs together.  But this has to be done manually.
        Hspec does not provide a way to automatically discover and run
        all specs of a project.
\end{itemize}
\end{quote}

>>>>

It is a common convention to have one spec file for each source file.
To run all specs for a given project together, it is necessary to
combine all the specs from all spec files into a single spec.  For
example, if we have three modules, \verb|Foo|, \verb|Foo.Bar| and
\verb|Baz|, and corresponding specs in \verb|FooSpec|,
\verb|Foo.BarSpec| and \verb|BazSpec|, we are required to write the
following boilerplate:

\noindent This is neither challenging nor interesting, so it should be
automated.  But Hspec does not provide a solution for that.
